A novel 1000\,MW double-reheat ultra-supercritical system with turbine-extraction-heated air preheaters and low-temperature economizers

### 2018-04-25 article.tex
基本完成引言部分的修改

% Nowadays ultra-supercritical (USC) power plants with large capacities and high parameters are considered to be feasible ways to save energy; as such, their usage has spread rapidly worldwide.
% The double-reheat USC unit is a new generation of USC unit that can improve thermal performance when compared with a single reheat unit~\cite{Zhao2017Exergy}. 
% According to~\cite{Zhao2017Exergy}, a double-reheat unit with the inlet parameter 30.0\,MPa/600/620/620$^\circ$C improves the heat efficiency by 2.4\%-2.6\% when compared with a commonly used USC unit with the inlet parameter 25.0\,MPa/600/600$^\circ$C.
%  The United States built the first double-reheat unit with the main parameter 34.4 MPa/649/566/566$^\circ$C in the 1960s.
%  Two 700 MW double-reheat USC units were put into operation in Japan in 1990. 
%  The process of building five double-reheat USC units began in China in 2012, and three of these units were put into operation in 2015.
%  Over the past few decades, double-reheat USC units have received increasing attention due to their rapid development worldwide.

@@

Liu et al.~\cite{Liu2017} investigated a 660 MW double-reheat unit and calculated the coal consumption decrease if the overheats of No.5 to No.10 extractions could be recovered.
Wang et al.~\cite{Wang2016} studied 1000MW double-reheat USC system adopting outer steam coolers to utilize the superheat of extraction steam and the influence of different extraction schemes on system efficiency.
% Zhou et al.~\cite{Zhou2016Parametric} carried out a parametric analysis and system optimization of double-reheat ultra-supercritical power plants based on exergy analysis and economic analysis. 
% The results showed that reasonable reheat parameters and reheat stage numbers can improve the double-reheat system's performance.
% Xu et al.~\cite{Xu2015Optimum} investigated the thermal performance of the steam and water cycle with a double reheat after the installation of an additional outer steam cooler (AOC).
The results showed that the AOC is an effective method of reducing the superheat degree and improving the efficiency of the unit.
Li et al.~\cite{Li2014Thermodynamic} proposed a system that uses ten-stage extractions and two outer steam coolers. 
The results of the thermodynamic and technical-economic analyses showed that this system can lower the cost of electricity to 55.89 USD/MWh.
In addition, Kjaer~\cite{Kjaer2010A} proposed a regenerative steam turbine for utilizing the superheat degree of the extractions.
In this design, part of the extraction from the turbine high pressure cylinder enters the additional regenerative steam turbine rather than the regenerative heater.
Extractions from the turbine intermediate pressure cylinder are replaced by those from the regenerative steam turbine.
The superheat degree of the extraction is significantly reduced in this design and the exergy destruction of regenerative heaters is likewise reduced, thereby resulting in an overall improvement in efficiency.
Xu et al.~\cite{Xu2015Optimum} compared two superheat utilization systems, one is with additional outer steam cooler (AOC) and the other one is with regenerative steam turbine.
The results showed that the system with regenerative steam turbine had a better techno-economic performance.

%虽然能够对蒸汽过热度进行利用，但是回热系统中换热器温差依旧很大。而利用锅炉烟气加热给水能够减少回热系统的换热温差

%对锅炉烟气余热的利用一直以来都是系统优化的重点。近年来部分学者提出的利用锅炉烟气加热给水方法提高系统效率，在该思路的指导下多种系统形式被提出：

To reuse the energy of the exhaust flue gas, Xu et al.~\cite{Xu2013Techno} proposed a low-pressure economizer (LPE) based on data compiled from some typical 1000\,MW power generation units in China. 
Four possible arrangements for LPE installation were proposed and their energy-saving effects were compared.
The results indicated that the LPE connected with the higher-temperature section of the condensate line created a greatest reduction in the standard coal equivalent (SCE).  
Wang et al.~\cite{Wang2012Application} investigated energy- and water-saving measures and the reduction of CO$_2$ after the installation of an LPE.
The results showed that the optimized measures can reduce SCE by 2-4\,g/kWh.
Stevanovic et al.~\cite{Stevanovic2014Efficiency} proposed an additional high-pressure economizer installed at a long-term running lignite-fired power plant.
The results showed that more than 30\,MW of the flue gas waste heat was recovered, creating an improvement in gross efficiency of 0.53\% and 9.4\,MW extra output power.
Xu et al.~\cite{Xu2013A} divided the air preheater into two stages to reduce the temperature difference in the heat transfer process.
A LPE was also installed between the two air preheaters to obtain an appropriate flue gas temperature range.
Thermodynamic and technical-economic analyses were conducted to reveal the performance improvement.
It was found that the SCE consumption was reduced by 6.7\,g/kWh.

The installation of an LPE also has some  other benefits, such as improvements in electrostatic precipitator collection efficiency~\cite{Li2016Low}.

现有研究往往关注与烟气余热温度与给水温度相匹配，并没有对锅炉中原有受热面进行优化。
为了能够对系统进行更加进一步的优化，用分析的方法被应用到热力系统优化中
In order to perform an in-depth analysis of the system, Zhao Z et al.~\cite{Zhao2017Exergy} studied the exergy distribution system for a 1000\,MW double-reheat USC power plant and determined the main causes of exergy destruction on the steam turbine.
Rashidi et al.~\cite{Rashidi2014Thermodynamic} performed a thermodynamic analysis of a double-reheat steam power plant.
According to Ref.~\cite{Wu2014Component}, component- and process-based exergy evaluations were performed on a coal-fired power plant in China, thereby helping researchers to identify energy-saving strategies.
It was pointed out that the exergy destruction in the heat transfer process accounts for the largest proportion of exergy destruction overall.

而通过火用分析，热力系统中锅炉损失占总用损失的70%，而空预器的损失和整个回热系统的损失相当。
降低空预器的用损失是实现系统用效率提升的重点
通过实现空气、汽轮机抽汽、锅炉省煤器出口烟气和冷凝水温度相匹配，够降低低锅炉用损失，提高系统效率。
这一点对于二次再热系统尤为重要，
所以在二次再热机组上进行多工质温度匹配分析对机组节能更具有潜力。

% Compared with the common USC system, the double-reheat system has some typical problems, such as the double-reheat ratio that is chosen and the high superheat degree of the first several extractions.
% Other common problems include the high boiler exhaust temperature, which leads to unreasonable energy-level matching and significant exergy destruction.

% Though the high live steam pressure and temperature of the USC unit improve its efficiency, there are still some imperfections that limit the improvement of the unit's performance.

% Given that boiler design and thermal system design belong to different research areas, boiler design is studied as a whole apart from the joint optimization of the boiler heat transfer process and regenerative process.

In this paper, a novel system based on a 1000\,MW double-reheat USC reference system is proposed to realize boiler and regenerative system energy cascade utilization. 
The novel system realized the reasonable temperature-matching of flue gas, air, extraction steam, and condensate water by using turbine-extraction-heating air preheaters (EAPHs) and low temperature economizer (LTEs).
Specifically, this study included the following tasks: (1) modeling the novel system and reference system with EBSILON® Professional; (2) using exergy analysis to compare both systems' exergy efficiency, exergy destruction distribution, and subsystem performance change; and (3) analyzing both systems' thermal performances under off-design conditions.

>>>>

@@

Liu et al.~\cite{Liu2017} investigated a 660 MW double-reheat unit and calculated the coal consumption decrease if the overheats of No.5 to No.10 extractions could be recovered.
Wang et al.~\cite{Wang2016} studied 1000MW double-reheat USC system adopting outer steam coolers to utilize the superheat of extraction steam and the influence of different extraction schemes on system efficiency.
The results showed that the AOC is an effective method of reducing the superheat degree and improving the efficiency of the unit.
Li et al.~\cite{Li2014Thermodynamic} proposed a system that uses ten-stage extractions and two outer steam coolers. 
The results of the thermodynamic and technical-economic analyses showed that this system can lower the cost of electricity to 55.89 USD/MWh.
In addition, Kjaer~\cite{Kjaer2010A} proposed a regenerative steam turbine for utilizing the superheat degree of the extractions.
In this design, part of the extraction from the turbine high pressure cylinder enters the additional regenerative steam turbine rather than the regenerative heater.
Extractions from the turbine intermediate pressure cylinder are replaced by those from the regenerative steam turbine.
The superheat degree of the extraction is significantly reduced in this design and the exergy destruction of regenerative heaters is likewise reduced, thereby resulting in an overall improvement in efficiency.
Xu et al.~\cite{Xu2015Optimum} compared two superheat utilization systems, one is with additional outer steam cooler (AOC) and the other one is with regenerative steam turbine.
The results showed that the system with regenerative steam turbine had a better techno-economic performance.
Although the above research can make use of extractions' high superheat degree, the loss in the regenerative subsystem is still very large.

In order to reduce the loss of the regenerative subsystem and use the heat of the boiler flue gas, the method of heating feed-water by boiler flue gas is proposed to improve the efficiency of the thermal system. 
Under the guidance of this idea, many kinds of system forms have been proposed.
Xu et al.~\cite{Xu2013Techno} proposed a low-pressure economizer (LPE) based on data compiled from some typical 1000\,MW power generation units in China. 
Four possible arrangements for LPE installation were proposed and their energy-saving effects were compared.
The results indicated that the LPE connected with the higher-temperature section of the condensate line created a greatest reduction in the standard coal equivalent (SCE).  
Wang et al.~\cite{Wang2012Application} investigated energy- and water-saving measures and the reduction of CO$_2$ after the installation of an LPE.
The results showed that the optimized measures can reduce SCE by 2-4\,g/kWh.
Stevanovic et al.~\cite{Stevanovic2014Efficiency} proposed an additional high-pressure economizer installed at a long-term running lignite-fired power plant.
The results showed that more than 30\,MW of the flue gas waste heat was recovered, creating an improvement in gross efficiency of 0.53\% and 9.4\,MW extra output power.
Xu et al.~\cite{Xu2013A} divided the air preheater into two stages to reduce the temperature difference in the heat transfer process.
A LPE was also installed between the two air preheaters to obtain an appropriate flue gas temperature range.
Thermodynamic and technical-economic analyses were conducted to reveal the performance improvement.
It was found that the SCE consumption was reduced by 6.7\,g/kWh.
The installation of an LPE also has some  other benefits, such as improvements in electrostatic precipitator collection efficiency~\cite{Li2016Low}.

The existing research of boiler flue gas heating feedwater has realized the matching of flue gas temperature and feedwater temperature.
In order to further optimize the system, the exergy analytical method is applied to the double reheat USC system by some researchers.
Zhao Z et al.~\cite{Zhao2017Exergy} studied the exergy distribution system for a 1000\,MW double-reheat USC power plant and determined the main causes of exergy destruction on the steam turbine.
Rashidi et al.~\cite{Rashidi2014Thermodynamic} performed a thermodynamic analysis of a double-reheat steam power plant.
According to Ref.~\cite{Wu2014Component}, component- and process-based exergy evaluations were performed on a coal-fired power plant in China, thereby helping researchers to identify energy-saving strategies.
It was pointed out that the exergy destruction in the heat transfer process accounts for the largest proportion of exergy destruction overall.
The largest part of the exergy loss is boiler, and the exergy loss of boiler's air preheater is equivalent to that of the whole regenerative subsystem.
Reducing the loss of air preheater is the key to improve the system's efficiency.

In this paper, the heat exchanging temperature match of air, turbine extractions, boiler economizer outlet flue gas and feedwater was fist proposed based on the existing researchof boiler flue gas heating feedwater, which could reduce the exergy loss of boiler and improve system efficiency.
This is remarkable effect for the double reheat thermal system. 
A novel system based on a 1000\,MW double-reheat USC reference system is proposed to realize boiler and regenerative system energy cascade utilization. 
The novel system realized the reasonable temperature-matching of flue gas, air, extraction steam, and condensate water by using turbine-extraction-heating air preheaters (EAPHs) and low temperature economizer (LTEs).
Specifically, this study included the following tasks: (1) modeling the novel system and reference system with EBSILON® Professional; (2) using exergy analysis to compare both systems' exergy efficiency, exergy destruction distribution, and subsystem performance change; and (3) analyzing both systems' thermal performances under off-design conditions.
